---
title: tardoc in your browser
---

This is R, running in this tab under [webR](https://docs.r-wasm.org/webr/latest/)
— no server, nothing installed. It builds a small `targets` pipeline, runs it, and
documents it with tardoc. Edit anything and press **Run**.

```{r}
#| comment: "#>"
proj <- file.path(tempdir(), "demo")
dir.create(file.path(proj, "R"), recursive = TRUE, showWarnings = FALSE)

writeLines(c(
  "#' Drop impossible readings",
  "#'",
  "#' @param x Raw readings.",
  "#' @param max_c Rated upper limit of the probe, in Celsius.",
  "#' @return The readings inside the probe's range.",
  "clean <- function(x, max_c = 85) {",
  "  # Out-of-range values mean a probe was being serviced, not that the",
  "  # station was really that hot. Dropping is deliberate.",
  "  x[x <= max_c]",
  "}"
), file.path(proj, "R", "functions.R"))

writeLines(c(
  "library(targets)",
  "tar_source('R')",
  "list(",
  "  tar_target(raw, { set.seed(1); round(rnorm(400, 20, 40), 1) },",
  "             description = 'Simulated logger export'),",
  "  tar_target(kept, clean(raw), description = 'Readings in range'),",
  "  tar_target(mean_c, mean(kept))",
  ")"
), file.path(proj, "_targets.R"))
```

`callr_function = NULL` is the whole trick: wasm cannot spawn a subprocess, so
the pipeline is read in this session instead.

```{r}
#| comment: "#>"
withr::with_dir(proj, targets::tar_make(callr_function = NULL))
```

```{r}
#| comment: "#>"
tardoc::document_targets(project_path = proj, pkg_name = "Browser pipeline")

list.files(file.path(proj, "tardoc"), recursive = TRUE)
```

The generated page for one function — roxygen above, source below, comments
intact:

```{r}
#| comment: ""
cat(readLines(file.path(proj, "tardoc", "functions", "clean.md")), sep = "\n")
```

Change the `max_c` default in `clean()`, press **Run** again, and watch `targets`
rebuild only what depends on it.
